---
title: "Data Science I Homework 1"
author: "Hongjie Liu"
output: github_document
---

Load the package `tidyverse` for homework 1.

```{r chunk_library, message = FALSE}
library(tidyverse)
```

## Problem 1

Load the `penguins` dataset.

```{r chunk_loaddataset}
data("penguins", package = "palmerpenguins")
```

Here is a short description of the `penguins` dataset:

* The names of the variables are ``r names(penguins)``. The values of the variable `species` are ``r unique(penguins$species)``. The values of the variable `island` are ``r unique(penguins$island)``. The values of the variable `year` are ``r unique(penguins$year)``.
* The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm=TRUE))` mm. (excluding missing values, rounded to integer)

Make a scatter plot to see the difference in flipper length and bill length between three species of penguins in the `penguins` dataset:

```{r chunk_scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

Save the scatter pot as a PDF file.

```{r chunk_saveplot}
ggsave("scatterplot_p8105_hw1_hl3640.pdf")
```

# Problem 2

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r chunk_dataframe}
p2_df = tibble(
  norm = rnorm(10),
  logical = norm > 0,
  char = c("Mercury", "Venus", "Earth", "Mars", "Ceres", "Jupiter", "Saturn", "Uranus", "Neptune", "Pluto"),
  factor = factor(c("< 2 AU", "< 2 AU", "< 2 AU", "< 2 AU", "2-15 AU", "2-15 AU", "2-15 AU", "> 15 AU", "> 15 AU", "> 15 AU"))
  )
```
