---
title: "Data Science I Homework 1"
author: "Hongjie Liu"
output: github_document
---

Load the package `tidyverse` for homework 1.

```{r chunk_library, message = FALSE}
library(tidyverse)
```


## Problem 1

Load the `penguins` dataset.

```{r chunk_loaddataset}
data("penguins", package = "palmerpenguins")
```

Here is a short description of the `penguins` dataset:

* The names of the variables are ``r names(penguins)``. The values of the variable `species` are ``r unique(penguins$species)``. The values of the variable `island` are ``r unique(penguins$island)``. The values of the variable `year` are ``r unique(penguins$year)``.
* The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm=TRUE))` mm. (excluding missing values, rounded to integer)

Make a scatter plot to see the difference in flipper length and bill length between three species of penguins in the `penguins` dataset:

```{r chunk_scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

Save the scatter pot as a PDF file.

```{r chunk_saveplot}
ggsave("scatterplot_p8105_hw1_hl3640.pdf")
```


## Problem 2

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r chunk_dataframe}
p2_df = tibble(
  norm = rnorm(10),
  logical = norm > 0,
  char = c("Mercury", "Venus", "Earth", "Mars", "Ceres", "Jupiter", "Saturn", "Uranus", "Neptune", "Pluto"),
  factor = factor(c("< 2 AU", "< 2 AU", "< 2 AU", "< 2 AU", "2-15 AU", "2-15 AU", "2-15 AU", "> 15 AU", "> 15 AU", "> 15 AU"))
  )
```

Try to take the mean of each variable in my dataframe.

```{r chunk_takingmean}
mean(pull(p2_df, norm))
mean(pull(p2_df, logical))
mean(pull(p2_df, char))
mean(pull(p2_df, factor))
```

Here are the results of applying the `mean` function to each variable:

* The function works when applied to the numeric variable `norm`.
* The function works when applied to the logical variable `logical`, because `TRUE` and `FALSE` can be interpreted as `1` and `0` respectively in R.
* The function does not work when applied to the character variable `char`.
* The function does not work when applied to the factor variable `factor`.

Next, apply the `as.numeric` function to the logical, character, and factor variables (output not displayed).

```{r chunk_applyfunction, results = 'hide', warning = FALSE}
as.numeric(pull(p2_df, logical))
as.numeric(pull(p2_df, char))
as.numeric(pull(p2_df, factor))
```

Here are the results of applying the `as.numeric` function:

* The function works when applying to the logical variable `logical`, because it converts `TRUE` and `FALSE` to `1` and `0` respectively.
* The function does not work when applying to the character variable `char`.
* The function works when applying to the factor variable `factor`, because it converts `"< 2 AU"`, `"> 15 AU"`, and `"2-15 AU"` to `1`, `2`, and `3` respectively. According to the description of `factor` function, the levels of a factor are by default sorted, but the sort order may well depend on the locale at the time of creation, and should not be assumed to be ASCII.