---
title: "Data Science I Homework 1"
author: "Hongjie Liu"
output: github_document
---

Load the package `tidyverse` for homework 1.

```{r chunk_library, message = FALSE}
library(tidyverse)
```

## Problem 1

Load the `penguins` dataset.

```{r chunk_loaddataset}
data("penguins", package = "palmerpenguins")
```

Here is a short description of the `penguins` dataset:

* The names of the variables are ``r names(penguins)``. The values of the variable `species` are ``r unique(penguins$species)``. The values of the variable `island` are ``r unique(penguins$island)``. The values of the variable `year` are ``r unique(penguins$year)``.
* The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm=TRUE))` mm. (excluding missing values, rounded to integer)

Make a scatter plot to see the difference in flipper length and bill length between three species of penguins in the `penguins` dataset:

```{r chunk_scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

Save the scatter pot as a PDF file.

```{r chunk_saveplot}
ggsave("scatterplot_p8105_hw1_hl3640.pdf")
```
